Density-dependent selection in evolutionary genetics: a lottery model of Grime's triangle

### 2016-12-20 manuscript.tex
latest

Each iteration, adults produce $m_i$ new offspring (henceforth called ``propagules''). We assume adults cannot be ousted from occupied territories, so only propagules landing on unoccupied territories are included in $m_i$. Dispersal is assumed to be unrestricted, so that all propagules have the same probability of landing on any of the $U$ unnocupied territories. Propagules disperse independently, and

 More generally, $m_i$ only includes propagules which actually end up contesting unnocupied territories. For simplicity, we assume $m_i=b_i n_i$, where $b_i$ is a constant, genotype-specific birth rate.

>>>>

Each iteration, adults produce $m_i$ new offspring (henceforth called ``propagules''). We assume adults cannot be ousted from occupied territories, so only propagules landing on unoccupied territories are included in $m_i$. Dispersal is random and unrestricted; each propagule has an equal probability of landing on any of the $U$ unnocupied territories. Loss of propagules during dispersal is subsumed into $m_i$ ($m_i$ only counts survivors which go on to contest the territory they land in), and we assume that propagules disperse independently of each other. In general, $m_i$ will increase with $n_i$, and will also depend on population density $N$. For example, if $b_i$ is the number of propagules produced per individual from genotype $i$, then $m_i=b_i(1-N/T)n_i$ would reflect the loss of propagules due to random dispersal to occupied territories. Nevertheless, for simplicity we will assume a linear function $m_i=b_i n_i$. Our justification is that the specific choice of $m_i$ makes little difference to our analysis here other than potentially complicating the mathematics. However, the choice of $m_i$ could matter in other applications, particularly when the mode of dispersal is a central concern [cite coexistence].
